DATA 621 - Business Analytics and Data Mining

### 2020-10-07 HW2/HW2-Group2.rmd
Sidestep singular/plural issue and whitespace

---
title: "DATA 621 - Business Analytics and Data Mining"
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg, Bryan Persaud,
  Jeff Shamp
date: "10/11/2020"
output:
  html_document: default
  pdf_document: default
subtitle: 'Fall 2020 - Group 2 - Homework #2'
---

@@

# 2. Confusion Matrix
A [confusion matrix](http://www.saedsayad.com/model_evaluation_c.htm) is a
format for summarizing the performance of a classification algorithm. It shows
the number of correct and incorrect predictions made by the classification model
and compares it to the actual outcomes in the data. The matrix is
\(N \times N\), where \(N\) is the number of target values. The following table
displays a \(2\times 2\) confusion matrix for two classes---positive and
negative. The actual confusion matrix is the 4 cells containing `a`, `b`, `c`,
and `d`. The enhancements around the matrix display the definitions for many
common classification metrics.

>>>>

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #2'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg, Bryan
  Persaud, Jeff Shamp
date: "10/11/2020"
output:
  pdf_document: default
  html_document: default
---

@@

# 2. Confusion Matrix
A [confusion matrix](http://www.saedsayad.com/model_evaluation_c.htm) is a
format for summarizing the performance of a classification algorithm. It shows
the number of correct and incorrect predictions made by the classification model
and compares it to the actual outcomes in the data. The matrix is
\(N \times N\), where \(N\) is the number of target values. The following table
displays a \(2\times 2\) confusion matrix for two classes---positive and
negative. The actual confusion matrix comprises the 4 cells containing `a`, `b`,
`c`, and `d`. The enhancements around the matrix display the definitions for
many common classification metrics.
